Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-05-02 paper.tex
Add hash distance distribution figure

While the validation loss is a reasonable indicator of network performance, its scale will vary depending on the $\alpha$ and $m$ regularization hyperparameters.
To obtain a more consistent metric, we also computed the distribution of distances between the pairs in $\mathcal{P}$ and those in $\mathcal{N}$.
If these distributions are well-separated, we can assume that the network is performing well.
We therefore used the Bhattacharyya distance between these distributions as an alternate performance metric \cite{bhattacharyya1943measure}.

The hashing networks for each modality were chosen to have the same architecture: A series of alternating convolutional and pooling layers followed by a series of fully-connected layers.
All convolutional and fully-connected layers used rectifier nonlinearities except the final output layer, which (as in \cite{masci2014multimodal}) used a hyperbolic tangent nonlinearity.
The first convolutional layer had 16 filters with a filter size of five beats by twelve semitones.
This choice was meant to provide some temporal context and octave invariance.
As advocated by \cite{simonyan2014very}, all subsequent convolutional layers had $2^{n + 3}$ 3x3 filters, where $n$ is the depth of the layer.
All pooling layers performed max-pooling, with a pooling size of 2x2.
Finally, as advocated by \cite{he2015delving}, we initialized all weights with normally distributed random variables with zero mean and a standard deviation of $\sqrt{2/n_{in}}$, where $n_{in}$ is the number of inputs to each layer.
Our model was implemented using Theano \cite{bastien2012theano} and \texttt{lasagne}.\footnote{\texttt{https://github.com/Lasagne/Lasagne}}

To ensure good performance, we optimized all model hyperparameters using Whetlab,\footnote{\texttt{http://www.whetlab.com}} a web API which implements black-box Bayesian optimization \cite{snoek2012practical}.
We used Whetlab to optimize the number of convolutional/pooling layers, the number and size of the fully-connected layers, the RMSProp learning rate and decay parameters, and the $\alpha$ and $m$ regularization parameters of $\mathcal{L}$.
As a hyperparameter optimization objective, we used the Bhattacharyya distance approach described above.
The best performing network found by Whetlab had 2 convolutional layers, 2 ``hidden'' fully-connected layers of with 2048 units in addition to a fully-connected output layer, a learning rate of .001 with a decay parameter of .65, and $\alpha = .5$ and $m = 4$.
This hyperparameter configuration yielded a Bhattacharya distance of $0.488$, indicating a strong separation between distances in $\mathcal{P}$ and distances in $\mathcal{N}$.
\textit{should maybe include a plot here of in-class/out-of-class distribution}

>>>>

While the validation loss is a reasonable indicator of network performance, its scale will vary depending on the $\alpha$ and $m$ regularization hyperparameters.
To obtain a more consistent metric, we also computed the distribution of distances between the hash vectors produced by the network for the pairs in $\mathcal{P}$ and those in $\mathcal{N}$.
If these distributions are well-separated, we can assume that the network is performing well.
We therefore used the Bhattacharyya distance between these distributions as an alternate performance metric \cite{bhattacharyya1943measure}.

The hashing networks for each modality were chosen to have the same architecture: A series of alternating convolutional and pooling layers followed by a series of fully-connected layers.
All convolutional and fully-connected layers used rectifier nonlinearities except the final output layer, which (as in \cite{masci2014multimodal}) used a hyperbolic tangent nonlinearity.
This choice allows us to obtain binary hash vectors by testing whether each output unit is greater or less than zero.
The first convolutional layer had 16 filters with a filter size of five beats by twelve semitones, which gives our network some temporal context and octave invariance.
As advocated by \cite{simonyan2014very}, all subsequent convolutional layers had $2^{n + 3}$ 3x3 filters, where $n$ is the depth of the layer.
All pooling layers performed max-pooling, with a pooling size of 2x2.
Finally, as advocated by \cite{he2015delving}, we initialized all weights with normally distributed random variables with zero mean and a standard deviation of $\sqrt{2/n_{in}}$, where $n_{in}$ is the number of inputs to each layer.
Our model was implemented using Theano \cite{bastien2012theano} and \texttt{lasagne}.\footnote{\texttt{https://github.com/Lasagne/Lasagne}}

To ensure good performance, we optimized all model hyperparameters using Whetlab,\footnote{\texttt{http://www.whetlab.com}} a web API which implements black-box Bayesian optimization \cite{snoek2012practical}.
We used Whetlab to optimize the number of convolutional/pooling layers, the number and size of the fully-connected layers, the RMSProp learning rate and decay parameters, and the $\alpha$ and $m$ regularization parameters of $\mathcal{L}$.
As a hyperparameter optimization objective, we used the Bhattacharyya distance approach described above.
The best performing network found by Whetlab had 2 convolutional layers, 2 ``hidden'' fully-connected layers of with 2048 units in addition to a fully-connected output layer, a learning rate of .001 with a decay parameter of .65, and $\alpha = .5$ and $m = 4$.
This hyperparameter configuration yielded the output hash distance distributions for $\mathcal{P}$ and $\mathcal{N}$ shown in Figure \ref{fig:distances}, which resulted in a Bhattacharryya distance of $0.488$.

\begin{figure}
  \includegraphics[width=\columnwidth]{hash_distributions.pdf}
  \caption{Output hash distance distributions for our best-performing network.}
  \label{fig:distances}
\end{figure}
